% Section unchanged
\section{Projects}
\subsection{Latex CV Builder}{Personal Project, \href{https://github.com/Danial-Kord/Latex-CV-Builder}{project link}}{2022 - now}
\begin{itemize}
    \item Developed a full-stack resume generator that converts JSON data to PDF using \textbf{Java + Spring Boot} microservices and \textbf{Django}, containerized with Docker and deployed on \textbf{AWS ECS}.
    \item Integrated \textbf{LangChain} and \textbf{n8n} for automated LLM-based resume customization workflows, and deployed a \textbf{React/Next.js} frontend via Vercel with monitoring and error handling.
\end{itemize}



\subsection{DigiHuman}{Open Source Thesis Project, \href{https://github.com/Danial-Kord/DigiHuman}{project link}}{2022 - 2023}
\begin{itemize}
    \item Created an open-source real-time animation system (500+ GitHub stars) for 3D avatars using Unity3D, Flask, and Blender, integrating motion capture with generative models.
    \item Enhanced spatial stability by fusing \textbf{BlazePose}, \textbf{FaceMesh}, and \textbf{MediaPipe} with low-pass and Kalman filters for facial/pose tracking across angles.
    \item Built a distributed processing pipeline handling 30 FPS motion data and added real-time performance diagnostics for rendering bottlenecks.
\end{itemize}


% \subsection{Techu}{TechuOnTheChair, \href{https://techuonthechair.com}{project website}}{2023}
% \begin{itemize}
%     \item Contributed to the development of "Techu," a 2D strategic card game for Android and IOS platforms, and created an AI-based player with a high win rate. \emph{Utilized} reinforcement learning principles for AI strategy development. 
%     \item Implemented online multiplayer mode and in-game statistics using Photon and PlayFab, \textbf{enhanced} player engagement and competitive gameplay. Used Firebase for push notifications, Analytics, etc.
%     \item Added In-app purchase through Google Services and integrated with Playfab for fraud detection. 
% \end{itemize}
\subsection{Panorama Image Reconstruction}{Academic Project, \href{https://github.com/Danial-Kord/Panorama}{project link}}{2023}
\begin{itemize}
    \item Generated panorama images from a sequence of photographs using Python and OpenCV. \emph{Implemented} algorithms to match SIFT features and calculate the optimal homography matrix with RANSAC, produced seamless panoramic images.
\end{itemize}

\subsection{PISE: Person Image Synthesis and Editing}{Academic Project, \href{https://github.com/Negiiiin/PISE}{project link}}{2023}
\begin{itemize}
    \item Reimplemented the CVPR 2021 paper "PISE: Person Image Synthesis and Editing with Decoupled GAN," and focused on human pose transfer challenges used in virtual reality and image editing.
    \item Used \textbf{PyTorch} and the DeepFashion In-shop Clothes Retrieval Benchmark dataset to replicate the results.
    % \item Addressed technical challenges such as pose mapping and occlusions by employing a two-stage generative process, and combined a human parsing map with the target pose for improved synthesis.
\end{itemize}



\subsection{\newline Solar System Simulation}{Personal Project, \href{https://github.com/Danial-Kord/Solar-System-OpenGL}{project link}}{2022}
\begin{itemize}
    \item Designed and developed a simulation of the solar system using C++ and OpenGL, implementing optimization techniques to efficiently render celestial bodies while maintaining consistent frame rates.
\end{itemize}




% \subsection{\newline  Harris Corner Detector}{Sharif University of Technology, \href{https://github.com/Danial-Kord/Harris-Corner-Detector}{project link}}{2023}
% \begin{itemize}
%     \item Developed the Harris Corner Detector from scratch using SIFT and RANSAC.
%     \item Implemented algorithms to detect corners of images by calculating the derivatives in x and y directions.
% \end{itemize}

% \subsection{3D Object Reconstruction}{Academic Project}{2023}
% \begin{itemize}
%     \item Executed feature extraction and 3D reconstruction of objects using Python and OpenCV. \emph{Applied} SIFT for extracting features and RANSAC for finding correspondences, \textbf{generated} accurate 3D models from 2D images.
%     \item Added the SOT deep learning model (PoinTr) for up-sampling point clouds, which \textbf{improved} model precision and detail.
% \end{itemize}

\subsection{Backgammon 3D}{Team Project, \href{https://youtu.be/54Xh9yhKRNs}{Demo link}}{2021}
\begin{itemize}
    \item Engineered a turn-based multiplayer online service game with matchmaking system and implemented Monte Carlo algorithm for AI decision-making, significantly improving game dynamics.
    % \item Created logging and monitoring systems for game state analysis, enabling efficient debugging and performance optimization during online gameplay.
\end{itemize}



\subsection{Urlshortener SaaS}{Personal Project, \href{https://github.com/Danial-Kord/Cloud-Computing-Project.git}{project link}}{2021}
\begin{itemize}
    \item Built a scalable URL shortener platform using \textbf{Java, MySQL, Docker, and Kubernetes} with a microservice architecture for high reliability and modular deployment.
    \item Used Hadoop as part of a backup and redundancy layer for distributed storage and fault tolerance.
\end{itemize}


\subsection{AI Algorithms Visualization}{Personal Project, \href{https://github.com/Danial-Kord/Artificial-Intelligence-Visualization}{project link}}{2021}
\begin{itemize}
    \item Developed educational visualizations of AI algorithms (e.g., graph search) using Python and the \textbf{Manim} animation library.
    \item Designed animated content to assist in teaching and self-learning of complex algorithmic concepts.
\end{itemize}


\subsection{Search Engine Development}{Academic Project, \href{https://github.com/Danial-Kord/Information_Retrieval_Search_Engine}{project link}}{2020}
\begin{itemize}
    \item Designed and implemented a search engine from scratch using Python, and focused on tf-idf, champion lists, and KNN/K-means algorithms. \emph{Aimed at} optimizing query response times and accuracy.
    \item \textbf{Improved} search result relevance and efficiency through effective pre-processing and indexing strategies.
\end{itemize}

\subsection{Multi-Core Computing Course}{Academic Project}{2020}
\begin{itemize}
    \item Explored parallel computing concepts by developing applications with C, OpenMP, and CUDA. \emph{Focused on} leveraging multi-core CPU and GPU architectures for performance gains in computational tasks.
\end{itemize}

\subsection{Sitadu}{Academic Project}{2020}
\begin{itemize}
    \item Developed a restaurant database management application to handle transactions, food services, and administrative tasks.
    \item Used JavaFX for building the user interface and JDBC for database connectivity, which enabled seamless data handling.
    \item Designed a robust backend system using MySQL to ensure efficient database operations and data storage.
\end{itemize}

% \subsection{Stone Thrower WebGL Game}{Internship Project, \href{https://danial-kord.github.io/StoneThrower}{project link}}{2020}
% \begin{itemize}
%     \item Developed a WebGL multiplayer game for café recreational activities, and delivered real-time gaming via web browsers.
%     \item Implemented networking and multiplayer mechanics using GoLang to enhance player engagement.
% \end{itemize}

% \subsection{RingBall Hyper Casual Game}{Team Project}{2019}
% \begin{itemize}
%     \item Created a hyper-casual IOS game, which was published on App Store, where players navigated a ball through obstacles. \emph{Utilized} Unity3D and a 3D mesh pathfinding algorithm for dynamic obstacle generation and movement.
% \end{itemize}


\subsection{XV6 Customization}{Academic Project, \href{https://github.com/Danial-Kord/XV6}{project link}}{2019}
\begin{itemize}
    \item Customized the XV6 operating system by adding new system calls and modifying CPU scheduling algorithms. \emph{Aimed at} understanding low-level OS functionalities and enhancing kernel features.
\end{itemize}

% \subsection{LittleBounty}{Team Project}{2019}
% \begin{itemize}
%     \item Developed a multiplayer online 2D game where teams competed to capture the enemy's flag. \emph{Implemented} server-client communication using Java, and supported both UDP and TCP protocols.
%     \item Orchestrated engaging game mechanics and networked multiplayer experience, \textbf{bolstered} teamwork and strategic gameplay.
% \end{itemize}

% \subsection{E' Gadung}{Freelance Project, \href{https://play.google.com/store/apps/details?id=com.liliannnco.gadungtale}{project link}}{2021}
% \begin{itemize}
%     \item Programmed a 2D platformer game in Unity, featuring multiple levels and enemies. \emph{Focused on} storytelling and character development to engage players in the game's narrative.
%     \item Successfully published the game on Google Play, \textbf{expanded} reach to a broader audience and received positive feedback.
% \end{itemize}